\documentclass[11pt,a4paper]{article}

% ----------------------- Packages -----------------------
\usepackage[margin=1.6cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}

% ----------------------- Formatting -----------------------
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

% Section title style
\titleformat{\section}%
{\Large\bfseries}%    Format
{}%                    Label
{0pt}%                 Sep
{#1}%  Before-code
[\vspace{2pt}\titlerule]%



% Bullet style
\newcommand{\redbullet}{\textcolor{red}{\large\textbullet}}

% Itemize style
\setlist[itemize]{nosep, left=12pt, label=\redbullet}

% ----------------------- Header -----------------------
\newcommand{\headerline}{
	\vspace{-8pt}
	\hrule height 0.8pt
	\vspace{8pt}
}

% ----------------------- Document -----------------------
\begin{document}
	
	% ----------------------- Name -----------------------
	\headerline
	\begin{center}
		{\Huge\bfseries Sohan Sethi}
		
		\vspace{4pt}
		\faEnvelope\ \, Chicago, IL \hspace{1cm}
		\faLinkedin\ \href{https://linkedin.com/in/sohansethi}{linkedin.com/in/sohansethi}
	\end{center}
	\headerline
	
	% ----------------------- EDUCATION -----------------------
	\section{EDUCATION}
	
	\textbf{University of Illinois at Chicago} \hfill \textit{Jan 2022 -- May 2023}\\
	\textit{Master of Science in Business Analytics, GPA: 3.91/4.0} \hfill \textit{Chicago, IL}\\
	Coursework: Data Mining, Statistics, Data Visualization, Healthcare Analytics, Strategy Consulting, Project Management
	
	\textbf{Mumbai University} \hfill \textit{Aug 2016 -- Oct 2020}\\
	\textit{Bachelor of Engineering in Computer Science} \hfill \textit{Mumbai, India}\\
	Coursework: Advanced Database Management, Software Development, Machine Learning, Management Information Systems
	
	
	% ----------------------- SKILLS -----------------------
	\section{SKILLS}
	
	\textbf{Analysis \& Visualization Tools:} Power BI, Tableau, Microsoft Excel, Looker, Visio, Alteryx, Hadoop, Google Analytics\\
	\textbf{Programming Languages:} SQL, Python, R, SPSS, Java, SAS, SAP\\
	\textbf{Database Management Systems:} SQL Server, MySQL, Oracle, PostgreSQL, NoSQL, SSRS, SSIS, MongoDB
	
	
	% ----------------------- EXPERIENCE -----------------------
	\section{EXPERIENCE}
	
	\textbf{Health Care Service Corporation} \hfill \textit{Aug 2023 -- Present}\\
	\textit{Business Analyst II} \hfill \textit{Chicago, IL}
	\begin{itemize}
		\item Performed data analysis on group insurance accounts to provide data-driven insights for BCBS leadership.
		\item Developed and integrated a performance reporting KPI metrics dashboard using Power BI.
		\item Designed automated reporting to calculate end-to-end cycle time using advanced DAX formulas.
		\item Spearheaded multiple new data collection processes using SharePoint and Power Automate.
		\item Designed and curated cross-platform web-app for interdepartmental usability using PowerApps.
	\end{itemize}
	
	\textbf{Discovery Partners Institute (UIC)} \hfill \textit{May 2022 -- May 2023}\\
	\textit{Research Assistant – Data Science} \hfill \textit{Chicago, IL}
	\begin{itemize}
		\item Conducted market research and industry analysis using Python for the applied R\&D department.
		\item Assessed the impact and effectiveness of inter-department processes, increasing KPIs by 30\%.
		\item Curated business plans that helped secure \$20M in funding.
	\end{itemize}
	
	\textbf{Net Square Solutions} \hfill \textit{Oct 2020 -- Dec 2021}\\
	\textit{Business Analyst} \hfill \textit{Mumbai, India}
	\begin{itemize}
		\item Performed descriptive, predictive, and prescriptive analysis on cybersecurity datasets.
		\item Prepared and analyzed sales reports tracking KPIs using Tableau, increasing product sales by 30\%.
		\item Improved communication between clients and development teams, exceeding quarterly goals by 67\%.
		\item Built an automated ETL pipeline in SQL increasing data processing efficiency by 45\%.
	\end{itemize}
	
	
	% ----------------------- PROJECTS -----------------------
	\section{PROJECTS}
	
	\textbf{Bank Loan Default Prediction} \hfill \textit{Aug 2022 -- Dec 2022}\\
	\textit{RStudio, Data Mining}
	\begin{itemize}
		\item Analyzed financial data for 100,000 borrowers using RStudio to conduct loan default analysis.
		\item Achieved 96\% accuracy using Random Forest and XGBoost models.
	\end{itemize}
	
	\textbf{Heart Disease Prediction Modeling} \hfill \textit{Aug 2022 -- Dec 2022}\\
	\textit{Python, SQL, Tableau, Spark}
	\begin{itemize}
		\item Examined heart disease data of 1.3M patients to determine future risk.
		\item Developed ML models (Random Forest, SVM) predicting with 92\% accuracy.
	\end{itemize}
	
	\textbf{Airline Comparison Analysis} \hfill \textit{Mar 2022 -- May 2022}\\
	\textit{Tableau and MS Excel}
	\begin{itemize}
		\item Investigated airline performance using Tableau, analyzing 3.9M American Airlines flights.
		\item Developed 27 dashboards identifying delays and comparing performance with Delta.
	\end{itemize}
	
	
	% ----------------------- LEADERSHIP -----------------------
	\section{LEADERSHIP \& AWARDS}
	
	\begin{itemize}
		\item Nominated for the Chancellor’s Award at UIC for academic excellence and contributions.
		\item Co-led construction of a primary school in Tanzania through the United Nations.
	\end{itemize}
	
\end{document}
