\documentclass[a4paper,10pt]{article}
\usepackage[margin=1.4cm]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=10pt, itemsep=2pt}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}

\begin{document}
	
	\begin{center}
		{\Large \textbf{Jabel Resendiz}} \\
		FullStack Developer | Software Engineer | AI Engineering \\[2pt]
		Email: \href{mailto:jabelresendiz03@gmail.com}{jabelresendiz03@gmail.com} \\
		GitHub: \href{https://github.com/JabelResendiz}{github.com/JabelResendiz} \\
		LinkedIn: \href{https://www.linkedin.com/in/jabel-resendiz-aguirre-26123a261}{linkedin.com/in/jabel-resendiz} \\
	\end{center}
	
	% --------- SUMMARY ----------
	\section*{Professional Summary}
	FullStack developer with strong algorithmic foundations (ICPC Finalist) and experience across frontend, backend, distributed systems, REST APIs and data engineering. Skilled in React, Vue.js, .NET, Python, SQL and scalable architectures. Seeking full-time opportunities in software engineering and fullstack development.
	
	% --------- SKILLS ----------
	\section*{Technical Skills}
	
	\textbf{Frontend:} React, Vue.js, Angular, Blazor, HTML, CSS, JavaScript, TypeScript \\
	\textbf{Backend:} C\#, .NET, Python, Node.js (Express), Go \\
	\textbf{Databases:} MySQL, PostgreSQL, SQL, relational design \\
	\textbf{FullStack:} REST APIs, state management, authentication, API integration \\
	\textbf{AI \& Data:} NLP, RAG, embeddings, data analysis (pandas), basic ML \\
	\textbf{Distributed Systems:} TCP/IP, concurrency, HDFS, Spark, Kafka \\
	\textbf{Tools:} Git, GitHub, Docker, Linux, VS Code, LaTeX \\
	
	% --------- PROJECTS ----------
	\section*{Projects}
	
	\textbf{Big Data SNP Genome Simulation Pipeline} — Spark + HDFS + Kafka (2025) \\
	Distributed platform for large-scale SNP simulation and processing. Kafka for streaming ingest, Spark for distributed analytics, HDFS for resilient storage, and Flask + WebSockets dashboard for real-time metrics visualization.
	
	\textbf{Peer-to-Peer BitTorrent System} (2025) \\
	Simplified BitTorrent-style distributed system with peer discovery, piece exchange, TCP/UDP transport, and SHA-256 integrity verification.
	
	\textbf{HULK Programming Language Compiler} (2023) \\
	C (Flex/Bison) compiler frontend with LLVM IR backend. Includes interpreter and basic optimizations.
	
	\textbf{Technical Write-Off API System} (2024) \\
	Backend in .NET + MySQL using Clean Architecture for inventory automation.
	
	\textbf{Enterprise Web Platform} (2024) \\
	Vue.js application integrated with REST APIs; reusable component architecture.
	
	% --------- EXPERIENCE ----------
	\section*{Experience}
	
	\textbf{CITMATEL} — Software Developer Intern \hfill Apr 2024 – Jun 2025
	\begin{itemize}
		\item Implemented features for payroll and internal tooling using .NET and SQL.
		\item Performed refactoring, debugging, testing and release preparation (Agile).
	\end{itemize}
	
	\textbf{SEGURMÁTICA} — Software Engineer (Antivirus Engine) \hfill Mar 2024 – Oct 2024
	\begin{itemize}
		\item Reverse engineering and static/dynamic malware analysis.
		\item Contributed to detection rules and core engine improvements.
	\end{itemize}
	
	% --------- EDUCATION ----------
	\section*{Education}
	\textbf{B.Sc. in Computer Science} — University of Havana \hfill 2022–2026 \\
	GPA: 4.89/5
	
	% --------- AWARDS ----------
	\section*{Awards}
	ICPC Caribbean Finalist (2024) \\
	Silver Medal — Central American Math Olympiad (2019) \\
	Bronze Medal — Ibero-American Math Olympiad (2020, 2021)
	
	% --------- LANGUAGES ----------
	\section*{Languages}
	Spanish (Native), English (Intermediate B1)
	
\end{document}
